A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-16 paper.tex
Started working on experiment 1

% packages
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algorithmicx} % Doc is at http://tug.ctan.org/macros/latex/contrib/algorithmicx/algorithmicx.pdf
\usepackage{algpseudocode}
%\newtheorem*{theorem}{Lemma}

%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amsthm}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\newtheorem*{theorem}{Theorem}

@@

As mentioned before, norm selection in $\mathbb{R}^n$ has a critical
impact on the compression error and ratio. To appreciate this effect,
let us consider the comparison between the infinity norm and the
Euclidean norm in dimension 2. By comparing the unit disk to the unit
square, we obtain that the compression ratio of a random stream would
be $\frac{4}{\pi}$ times larger with the infinity norm than with the
Euclidean norm. Conversely, a compression error bounded by $\epsilon$
with the infinity norm corresponds to a compression error of
$\frac{\epsilon}{\sqrt{2}}$ with the Euclidean norm. Unsurprisingly, the
infinity norm is more 'tolerant' than the Euclidean norm.

@@

\section{Results}
\todo{ result table ?}
\subsection{Experiment 1: Pilot tests on Computer}
In this experiment, in order to compare the performance in different norm, different EPSILON and different dataset. We collected 2 data set from Neblina, 5-times bicep curl data and Mohammad Lateral bicep curl.
\begin{itemize}
    \item Data set: 5-times bicep curl which includes 613 data;
                    Mohammad Lateral bicep curl which include 41428 data;
                    All data is collected from Neblina, with 50Hz sampling of Sensors.
                    Using Valgrind massif measure memory usage. And using 'gettimeofday()' function in 'sys/time.h' for measure processing time usage.
    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
    \item Result: From the table 1 and table 2, The Max Error, Compression Radio and Time usage in both norm decrease when EPSILON become smaller. Comparing with different norm and same EPSILON, the infinity no, and few ndeed has more 'tolerance'. But when comparing using Infinity with $\epsilon=100/\sqrt{n}$, where n is number of dimension, to make sure the max error would not greater than 100, and Euclidean with $\epsilon$=100, the Euclidean norm has better compression radio. Although Infinity norm makes Max error larger, but it has less running time, and few fixed Memory usage according number of dimension. The Memory Usage of Euclidea is not fixed, because it need save $\mathcal{B}_i, i\subset\llbracket 1, m \rrbracket$ after origin $(u_0^k, y_0^k)$, costing lots of Memory. From the table 1 and 2, the Compression Radio in second data set is pretty better than first data set, because Mohammad Lateral bicep has more data than first dataset about 67.5 times. It is pointless to consider the different compression radio in this situation.

    \item Conclusion: The infinity norm has higher compression radio than Euclidean norm with same $\epsilon$, and uses less running time and little memory. But Euclidean makes sure the Max Error between reconstructed data and original data under EPSILON. Both of norm would has lower Compression ratios when $\epsilon$ becomes smaller.
\end{itemize}

\subsection{Experiment 2: energy reduction on the Neblina}
The experiment in Neblina V2 module~\cite{Neblina}, which is a module integrating multiple sensors. Its current System-on-Chip (SoC) radio is the Nordic Semiconductor nRF52832, and it has 64KB RAM.

@@

\section*{Acknowledgement}
\begin{table*}[]
    \begin{center}
    \caption{Result of Experiment 1 in Dimension 2}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
    Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
    Epsilon                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$  & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ \hline
    Max Error              & 127.63       & 94.46           & 99.63       & 70.47           & 140.70     & 99.73             & 99.99      & 70.71             \\ \hline
    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%         & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ \hline
    Max memory Usage(peak) & 80B          & 80B             & 432B        & 240B            & 80B        & 80B               & 2.1KB      & 1.3KB             \\ \hline
    Time Usage(Total)      & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms         & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
    \end{tabular}
    \end{center}
\end{table*}

\begin{table*}[]
    \begin{center}
    \caption{Result of Experiment 1 in Dimension 3}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
    Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
    Epsilon                & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$  & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\ \hline
    Max Error              & 141.66       & 85.40           & 99.94       & 56.89           & 168.95     & 97.01             & 99.99      & 57.73             \\ \hline
    Compression Radio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%          & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\ \hline
    Max memory Usage(peak) & 112B         & 112B            & 384B        & 256B            & 112B       & 112B              & 4.9KB      & 3.0KB             \\ \hline
    Time Usage(Total)      & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms         & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
    \end{tabular}
    \end{center}
\end{table*}

>>>>

% packages
\usepackage{algorithm}
\usepackage{algorithmicx} % Doc is at http://tug.ctan.org/macros/latex/contrib/algorithmicx/algorithmicx.pdf
\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage{colortbl} % for \rowcolor
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amsthm}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newtheorem*{theorem}{Theorem}
\definecolor{headcolor}{gray}{0.9}

@@

As mentioned before, norm selection in $\mathbb{R}^n$ has a critical
impact on the compression error and ratio. To appreciate this effect,
let us consider the comparison between the infinity norm and the
Euclidean norm in dimension 2. By comparing the unit disk to the unit
square, we obtain that the compression ratio of a random stream would
be $\frac{4}{\pi}$ times larger with the infinity norm than with the
Euclidean norm. Conversely, a compression error bounded by $\epsilon$
with the infinity norm corresponds to a compression error of
$\frac{\epsilon}{\sqrt{n}}$ with the Euclidean norm. Unsurprisingly, the
infinity norm is more 'tolerant' than the Euclidean norm.

@@

\section{Results}

We conducted two experiments using Motsai's Neblina 
module\footnote{\url{ https://motsai.com/products/neblina}}, a system 
with a Nordic Semiconductor nRF52832 micro-controller, 64~KB of RAM, 
and Bluetooth Low Energy connectivity. The Neblina has a 3D 
accelerometer, 3D gyroscope, 3D magnetometer, and environmental sensors 
for humidity, temperature and pressure. It can function as an Inertial
Motion Unit, a Vertical Reference Unit, or an Attitude and Heading Reference
System.

\subsection{Experiment 1: validation tests}

In this experiment we validated the behavior of our LTC extensions on a 
PC processing data acquired with the Neblina. We collected 2 data sets, 
``5-times biceps curl" and ``Mohammad lateral biceps curl". from the 
accelerometer with a 50Hz sampling rate (see 
Figure~\ref{fig:datasets}).

We compressed the datasets with various values of $\epsilon$, using our 
2D (x and y) and 3D (x, y and z) implementations of LTC. On the Neblina,
the resolution of the accelerometer is about 20~mg (196~mm/$s^2$).
 We used a 
laptop computer with 16~GB of memory, and Intel i5-3210M CPU @ 2.50GHz 
× 4, and Linux Fedora 27. We measured memory consumption using 
Valgrind's massif 
tool~\cite{nethercote2006building}\footnote{\url{http://valgrind.org}}, 
and processing time using \texttt{gettimeofday()} from the GNU C 
Library.

Results are reported in Table~\ref{table:results-validation}. 
As expected, the maximum measured error remains lower than $\epsilon$ in 
all cases, and the compression ratio increases with $\epsilon$. 
%Compared to the infinity norm, The Euclidean norm reduces the 
%compression ratio by a factor of \pm, which was also expected.

    %~ \item Result: From the table 1 and table 2, The Max Error, 
    %~ Compression Radio and Time usage in both norm decrease when EPSILON 
    %~ become smaller. Comparing with different norm and same EPSILON, the 
    %~ infinity no, and few ndeed has more 'tolerance'. But when comparing 
    %~ using Infinity with $\epsilon=100/\sqrt{n}$, where n is number of 
    %~ dimension, to make sure the max error would not greater than 100, 
    %~ and Euclidean with $\epsilon$=100, the Euclidean norm has better 
    %~ compression radio. Although Infinity norm makes Max error larger, 
    %~ but it has less running time, and few fixed Memory usage according 
    %~ number of dimension. The Memory Usage of Euclidea is not fixed, 
    %~ because it need save $\mathcal{B}_i, i\subset\llbracket 1, m 
    %~ \rrbracket$ after origin $(u_0^k, y_0^k)$, costing lots of Memory. 
    %~ From the table 1 and 2, the Compression Radio in second data set is 
    %~ pretty better than first data set, because Mohammad Lateral bicep 
    %~ has more data than first dataset about 67.5 times. It is pointless 
    %~ to consider the different compression radio in this situation.

    %~ \item Conclusion: The infinity norm has higher compression radio 
    %~ than Euclidean norm with same $\epsilon$, and uses less running 
    %~ time and little memory. But Euclidean makes sure the Max Error 
    %~ between reconstructed data and original data under EPSILON. Both of 
    %~ norm would has lower Compression ratios when $\epsilon$ becomes 
    %~ smaller.

\begin{table}

    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
    Norm                       & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
    $\epsilon$                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$ \\
    Max error              & 90.24       & 66.79           & 99.63       & 70.47          \\ 
    Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\ 
    Peak memory usage      & 80B          & 80B             & 432B        & 240B           \\ 
    Processing time        & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms        \\ \hline
    \end{tabular}
    \caption{5-times bicep curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
    Norm               & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$             & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ 
    Max error              & 99.49     & 70.52             & 99.99      & 70.71             \\ 
    Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
    Peak memory       & 80B        & 80B               & 2.1KB      & 1.3KB             \\ 
    Processing time      & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
    \end{tabular}
    \caption{Mohammad lateral biceps curl (2D)}
    \end{subfigure}\\    
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$             & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$   \\ 
    Max error              & 100.17       & 60.38           & 99.94       & 56.89            \\ 
    Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\ 
    Peak memory            & 112B         & 112B            & 384B        & 256B             \\ 
    Processing time        & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms          \\ \hline
    \end{tabular}
    \caption{5-times biceps curl (3D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$                & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\
    Max error                 & 97.54     & 56.00             & 99.99      & 57.73             \\
    Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
    Peak memory & 112B        & 112B              & 4.9KB      & 3.0KB             \\
    Processing time           & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
    \end{tabular}
    \caption{Mohammad lateral biceps curl (3D)}
    \end{subfigure}
    \caption{Validation experiment}
    \label{table:results-validation}
\end{table}

\subsection{Experiment 2: energy reduction on the Neblina}

@@

\section*{Acknowledgement}
